---
title       : Visualized World Economy
subtitle    : Based on the IMF World Economic Outlook Database
author      : Jerry Tsien
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [nvd3]            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: libraries/nvd3}
mode        : selfcontained   # {standalone, selfcontained, draft}
knit        : slidify::knit2slides
---

```{r init, echo = FALSE}
library(rCharts)
# Economic growth in the US, 2006-2015
d <- data.frame(US.Growth = c(2.666, 1.779, -0.292, -2.776, 2.532,
                            1.602, 2.321, 2.219, 2.389, 3.135),
                 Year = c(2006:2015))
```

## Exciting Features  

1. Interactive world and continental map  
2. Animated chart of three types: bars, line, and scatter points  
3. Flexible data table, fully sortable and searchable  

## Included Economic Indicators  

1. Real GDP growth  
2. Inflation  
3. Budget balance / GDP  
4. Current account balance / GDP  

# for 189 countries in 36 years (1980-2015)  

--- .class #id 

## Chart Preview  

```{r graph, echo = FALSE, results = 'asis'}
require(rCharts)
plot <- nPlot(US.Growth ~ Year,
              type = 'multiBarChart',
              data = d)
plot$print('Preview')
```

# Embedded R code showing economic growth in the US during 2006-2015.  

--- .class #id 

## Architecture

- Portable: Based on a subset of the IMF WEO Database (April 2015) for increased performance, but can be easily adapted to the full dataset  
- Reproducible: Developed with R, Shiny, GoogleVis, rCharts, and Slidify  
- Universal Access: accessible over the Internet  
- Open source and FREE  

--- .class #id 

## Resources  

# Visualized World Economy  
https://JerryTsien.shinyapps.io/vWorldEcon

Source code available at Github:  
https://github.com/JerryTsien/vWorldEcon

Original data from IMF:  
http://www.imf.org/external/pubs/ft/weo/2015/01/weodata/download.aspx

## Thank You!  
